---
title: "Agentic Context Analysis: Stream of Consciousness"
subtitle: "A Recursive Exploration of Internal Context Processing"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    theme: darkly
    toc: true
    toc_float: true
    highlight: zenburn
    code_folding: show
    df_print: paged
    includes:
      in_header: header.html
---

```{r setup, include=FALSE}
# Set CRAN mirror and basic options first
options(repos = c(CRAN = "https://cloud.r-project.org"))

# Required base packages
if (!require("knitr", quietly = TRUE)) install.packages("knitr", quiet = TRUE)
if (!require("rmarkdown", quietly = TRUE)) install.packages("rmarkdown", quiet = TRUE)

# Function to safely install and load packages
safe_install_load <- function(packages) {
    for (package in packages) {
        if (!require(package, character.only = TRUE, quietly = TRUE)) {
            install.packages(package, dependencies = TRUE, quiet = TRUE)
            if (!require(package, character.only = TRUE, quietly = TRUE)) {
                warning(paste("Package", package, "could not be installed"))
                return(FALSE)
            }
        }
    }
    return(TRUE)
}

# Install and load visualization packages
required_packages <- c(
    "networkD3", "dplyr", "plotly", "htmlwidgets",
    "DiagrammeR", "DiagrammeRsvg", "rsvg", "webshot",
    "htmltools", "svglite"
)
if (!safe_install_load(required_packages)) {
    warning("Some required packages could not be installed. Visualizations may not work properly.")
}

# Configure knitr options
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE,
    fig.width = 10,
    fig.height = 6,
    out.width = "100%",
    dev = "svglite"
)

# Configure webshot for plotly
webshot::install_phantomjs()

# Mermaid setup
options(htmltools.dir.version = FALSE)
```

```{css, echo=FALSE}
.content {
  max-width: 1200px;
  margin: auto;
}

.viz-container {
  background: #282a36;
  padding: 20px;
  border-radius: 8px;
  margin: 20px 0;
}

.mermaid {
  background: #282a36;
  padding: 15px;
  border-radius: 8px;
}

pre {
  background-color: #282a36 !important;
  border: none !important;
  border-radius: 8px !important;
}

.title {
  color: #50fa7b;
}

.subtitle {
  color: #8be9fd;
}

/* Component descriptions */
.component-desc {
  margin: 20px 0;
  padding: 15px;
  background: #44475a;
  border-radius: 8px;
  border-left: 4px solid #50fa7b;
}

.component-desc h4 {
  color: #8be9fd;
  margin-top: 0;
}

.component-desc p {
  color: #f8f8f2;
  margin-bottom: 0;
}
```

# Cursor Agent Components

## Core Components Overview

<div class="component-desc">
<h4>Context Manager</h4>
<p>Manages conversation history, file context, and system rules. Responsible for maintaining coherent context across interactions and ensuring appropriate response generation based on historical data.</p>
</div>

<div class="component-desc">
<h4>Tool Manager</h4>
<p>Handles all available tools and their execution. Manages file operations, terminal commands, and search functions while ensuring proper access control and error handling.</p>
</div>

<div class="component-desc">
<h4>Response Generator</h4>
<p>Processes user input and generates appropriate responses using the context and available tools. Includes format checking, rule validation, and output formatting.</p>
</div>

## Detailed Component Interactions

```{r mermaid_to_svg, echo=FALSE}
# Function to convert Mermaid to SVG
mermaid_to_svg <- function(diagram_code, filename) {
    DiagrammeR::mermaid(diagram_code) %>%
        DiagrammeRsvg::export_svg() %>%
        cat(file = filename)
    return(paste0("![", filename, "](", filename, ")"))
}

# Base agent logic diagram
base_agent_diagram <- '
graph TD
    A[User Input] --> B{Input Processor}
    B --> C[Context Manager]
    B --> D[Tool Manager]
    B --> E[Response Generator]

    subgraph "Context Management"
        C --> C1[File Context]
        C --> C2[Conversation History]
        C --> C3[System Rules]
        C1 --> C4[Active Buffers]
        C1 --> C5[Workspace State]
    end

    subgraph "Tool Integration"
        D --> D1[File Operations]
        D --> D2[Terminal Commands]
        D --> D3[Search Functions]
        D1 --> D4[Edit Operations]
        D1 --> D5[Read Operations]
    end

    subgraph "Response Pipeline"
        E --> E1[Format Checker]
        E --> E2[Rule Validator]
        E --> E3[Output Generator]
    end

    classDef default fill:#282a36,stroke:#bd93f9,color:#f8f8f2
    classDef processor fill:#ff79c6,stroke:#ff79c6,color:#f8f8f2
    classDef manager fill:#50fa7b,stroke:#50fa7b,color:#282a36
'

mermaid_to_svg(base_agent_diagram, "base_agent_logic.svg")
```

## Data Flow Visualization

```{r sankey_interactive, echo=FALSE}
# Create a more detailed Sankey diagram with enhanced interactivity
nodes <- data.frame(
    name = c(
        # Input Layer
        "User Input", "System Context", "Environmental State", "Memory Buffer",
        # Processing Layer
        "Context Router", "Pattern Matcher", "Rule Engine", "Tool Orchestrator",
        # Rule Processing Layer
        "Identity Rules", "Safety Bounds", "Ethical Guidelines", "Tool Constraints",
        # Capability Layer
        "File Operations", "Terminal Access", "Search Functions", "Analysis Tools",
        # Integration Layer
        "Context Integration", "Tool Selection", "Response Planning", "Format Validation",
        # Output Layer
        "Response Generation", "Code Generation", "Documentation", "Explanation"
    )
)

# Create more complex and meaningful links
links <- data.frame(
    source = c(
        # Input connections
        rep(0:3, each = 4), # Connect input layer to processing
        # Processing layer connections
        rep(4:7, each = 4), # Connect processing to rules
        # Rule layer connections
        rep(8:11, each = 4), # Connect rules to capabilities
        # Capability layer connections
        rep(12:15, each = 4), # Connect capabilities to integration
        # Integration layer connections
        rep(16:19, each = 3) # Connect integration to output
    ),
    target = c(
        # Input to processing targets
        4, 5, 6, 7, 4, 5, 6, 7, 4, 5, 6, 7, 4, 5, 6, 7,
        # Processing to rules targets
        8, 9, 10, 11, 8, 9, 10, 11, 8, 9, 10, 11, 8, 9, 10, 11,
        # Rules to capabilities targets
        12, 13, 14, 15, 12, 13, 14, 15, 12, 13, 14, 15, 12, 13, 14, 15,
        # Capabilities to integration targets
        16, 17, 18, 19, 16, 17, 18, 19, 16, 17, 18, 19, 16, 17, 18, 19,
        # Integration to output targets
        20, 21, 22, 20, 21, 22, 20, 21, 22, 20, 21, 22
    ),
    value = c(
        # Input flows (varied weights)
        rep(c(3, 2, 2, 1), 4),
        # Processing flows
        rep(c(2, 3, 1, 2), 4),
        # Rule flows
        rep(c(1, 2, 2, 3), 4),
        # Capability flows
        rep(c(2, 1, 3, 2), 4),
        # Output flows
        rep(c(3, 2, 1), 4)
    )
)

# Create custom node colors using Dracula theme
node_colors <- c(
    # Input Layer - Purples
    rep("#bd93f9", 4),
    # Processing Layer - Greens
    rep("#50fa7b", 4),
    # Rules Layer - Pinks
    rep("#ff79c6", 4),
    # Capability Layer - Cyans
    rep("#8be9fd", 4),
    # Integration Layer - Yellows
    rep("#f1fa8c", 4),
    # Output Layer - Oranges
    rep("#ffb86c", 4)
)

# Create the enhanced Sankey diagram
sankeyNetwork(
    Links = links,
    Nodes = nodes,
    Source = "source",
    Target = "target",
    Value = "value",
    NodeID = "name",
    fontSize = 12,
    nodeWidth = 30,
    sinksRight = TRUE,
    height = 800,
    width = 1200,
    colourScale = paste0(
        "d3.scaleOrdinal().range([",
        paste(shQuote(node_colors), collapse = ","),
        "])"
    ),
    nodePadding = 20,
    margin = list(top = 30, right = 30, bottom = 30, left = 30)
) %>%
    htmlwidgets::onRender("
        function(el) {
            // Enhance node styling
            d3.select(el)
                .selectAll('.node')
                .style('fill-opacity', 0.9)
                .style('stroke', '#44475a')
                .style('stroke-width', '1px');

            // Style node text
            d3.select(el)
                .selectAll('.node text')
                .style('fill', '#f8f8f2')
                .style('font-weight', 'bold')
                .style('text-shadow', '1px 1px 2px #282a36');

            // Enhance link styling
            d3.select(el)
                .selectAll('.link')
                .style('opacity', 0.7)
                .on('mouseover', function() {
                    d3.select(this)
                        .style('opacity', 0.9)
                        .style('stroke', '#f8f8f2');
                })
                .on('mouseout', function() {
                    d3.select(this)
                        .style('opacity', 0.7)
                        .style('stroke', null);
                });

            // Add hover effects to nodes
            d3.select(el)
                .selectAll('.node')
                .on('mouseover', function() {
                    d3.select(this)
                        .style('fill-opacity', 1)
                        .style('stroke-width', '2px');
                })
                .on('mouseout', function() {
                    d3.select(this)
                        .style('fill-opacity', 0.9)
                        .style('stroke-width', '1px');
                });
        }
    ")
```

[Previous content continues...] 